---
title: "autoNumCaptions: An R package for auto-numbering html and markdown figures"
author: "Keaton Stagaman"
date: "6/25/2019"
output: github_document
html_preview: true
always_allow_html: yes
---
```{r results="asis", echo=FALSE}
cat("
<style>
caption {
      font-size: 12px;
      text-align: left;
    }
</style>
")
```

```{r setup, include=FALSE}
library(ggplot2)
library(kableExtra)
library(autoNumCaptions)
df1 <- data.frame(X = 1:10, Y = (1:10)^2)
set.seed(42)
df2 <- data.frame(
  A = c("red", "green", "blue"), 
  B = round(rnorm(3), 4), 
  C = c("TRUE", "FALSE", "TRUE"),
  D = seq(0, 10, length.out = 3),
  E = c("North", "South", "West"),
  F = round(c(pi, pi^2, pi^pi), 4),
  G = round(rgamma(3, shape = 1), 4), 
  H = round(rbinom(3, 10, 0.5), 4)
)
```

## Installation

```
# install.packages("devtools")
devtools::install_github("kstagaman/autoNumCaptions")
```

## Usage

When generating HTML or Markdown files using `knitr`, utilizing the `caption` argument does not auto-number the figures or tables (as it does when producing a PDF through LaTeX). This package allows one to add auto-numbered captions directly to plots, ggplots, and tables. Furthermore, because captions are not automattically wrapped to fit in the plot space (`ggplot` doesn't wrap caption text), these functions wrap the text to a length (in columns) that can be specified by the user.

```{r ggplot-example}
my.theme <- theme_update(plot.caption = element_text(hjust = 0, vjust = 1, size = 10))
ggplot(df1, aes(x = X, y = Y)) +
  geom_point() +
  gg_figure_caption(caption = "This figure demonstrates how to add a caption to a ggplot")
```

```{r plot-example}
plot(
  df1$X, 
  df1$Y, 
  sub = figure.caption("This figure demonstrates how to add a caption to a base plot")
  )
```

```{r supp-ggplot-examples}
ggplot(df1, aes(x = X, y = Y)) +
  geom_point() +
  gg_figure_caption(
    caption = "This figure demonstrates how to add a caption to a supplemental ggplot",
    supplemental = TRUE
    )

ggplot(df1, aes(x = X, y = Y)) +
  geom_point() +
  gg_figure_caption(
    caption = "This figure demonstrates how to add a caption to a supplemental ggplot and use \"S\" in front of the number instead of \"Supplemental\" in front of \"Figure\"",
    supplemental = TRUE,
    s.numbers = TRUE
    )
```

```{r table-example}
kable(
  df2, 
  caption = table.caption("This table demonstrates how to add a caption to a kable table")
  ) %>% kable_styling(font_size = 12, bootstrap_options = "striped", full_width = T)
```

```{r supp-table-examples}
kable(
  df2, 
  caption = supp.tbl.caption(
    "This table demonstrates how to add a caption to a supplemental kable table"
    )
  ) %>% kable_styling(font_size = 12, bootstrap_options = "striped")

kable(
  df2, 
  caption = supp.tbl.caption(
    "This table demonstrates how to add a caption to a supplemental kable table and use \"S\" in front of the number instead of \"Supplemental\" in front of \"Table\"",
    s.numbers = TRUE
    )
  ) %>% kable_styling(font_size = 12, bootstrap_options = "striped")
```
